More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-01-29 2016-Weak-FH-Bisim/WeakBisim.tex

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$
~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{(\beta^3_p)},\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
and $ P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$

where for all $l\in L$:\\
$
s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$

We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred_p}\!\!',  
				{\Post_p}\!\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$

such that  $\Pred^1_p \iff {\Pred_p}\!\!'
		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post_p}\!\!'\uplus 
		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and \\
$P\models{\openrule
			{
				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^1_p},  
				{\Post^1_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

\item Similarly for tau transitions on states named $u$.

\item And, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post}\,'\uplus 
		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred}\,',  
				{\Post}\,'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}

By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

\TODO{We will add side conditions ?? }\\

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$.

Therefore, we will obtain:

$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
\TODO{We will discuss}

For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

\end{mathpar}
By rule (\WTTrois)  we can conclude that  we have:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.
\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\

For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ open transitions  $\symb{OT}_p$ s.t $p\in [0\ldots n]$.

Hence, we have forall $p\in [0\ldots n]$ :  
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

>>>>

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0\ldots m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$
s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
$\\
We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
				{{\Post^1_p}\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$

such that  $\Pred^1_p \iff {\Pred^1_p}\!'
		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^1_p}\!',  
				{\Post^1_p}\!'}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

\item Similarly, we use the same process on states named $u$.

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred^2 \iff {\Pred}\,'
		\land {\Pred^2}''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post^2}'\uplus 
		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^2}',  
				{\Post^2}'}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
\\
\Pred\,'=\bigwedge_{i=0}^{m_1}
{\Pred_i^1}'\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'\subst{{\Post^2}'})\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}\\
\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
$\\
\TODO{To check: ce n'est pas $m_1, m_2$ mais $m_1', m_2'$ such that 
 $m_1'= m_1\setminus\Holes(Q)$???}\\

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
				{\Post^2}''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0\ldots (n_1+n_2+2)]\,\, Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of  $\tau$ action containing only one observable action.  We can decompose each subsequence $k$ of length $len$  as follows:\\
$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
			{
				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
				{{\Post^1_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
				{{\Post^2}''}}
				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n'+1)\ldots (len-1)]\,\, Q\models{\openrule
			{
				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
				{{\Post^3_p}''}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$v_l=v_{0l} \wedge v_l'=v_{len}$\\
$\forall j \in {j\in (J\cap\Holes(Q))},\quad
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
\\
\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
$\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_p$ such that $p\in [0\ldots n]$.
Therefore, we can conclude that we have forall $p\in [0\ldots n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
\Post=\Post\,'\uplus\biguplus_{p=0}^n
		\Post_p \quad$

\TODO{I stopped there!}
\end{proof}
